Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-13 doc/manuscript/manuscript.Rmd
add R to Jim's name in author list

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amaradasa
    email: b.amaradasa@ufl.edu
    affiliation: 1
  - name: Rachana Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: Serena McCoy
    email: serena.mccoy@icloud.com
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln, NE 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
header-includes: |
  \usepackage{indentfirst}

>>>>

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amaradasa
    email: b.amaradasa@ufl.edu
    affiliation: 1
  - name: Rachana Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: Serena McCoy
    email: serena.mccoy@icloud.com
    affiliation: 1
  - name: James R. Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln, NE 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
header-includes: |
  \usepackage{indentfirst}
